---
title: "nyc-hhw"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
install.packages('viridis')
library(openxlsx)
library(rgdal)
library(maptools)
library(ggplot2)
library(plyr)
library(rgeos)
library(RColorBrewer)
library(ggthemes)
library(reshape2)
library(dplyr)
if (!require(gpclib)) install.packages("gpclib", type="source")
gpclibPermit()
library(viridis)
```

## TOP 2016 SF

### Run SQL Query

Top complaint 2016 SF is Bulky Items. 

```{sql top_2016_nyc}
#standardSQL
SELECT
complaint_type,
COUNT(descriptor) AS total_count
FROM
`bigquery-public-data.new_york.311_service_requests`
WHERE 
EXTRACT(year from created_date) = 2016
GROUP BY complaint_type
ORDER BY
2 DESC
```

### Results

```{r top_2016_nyc_results}

top2016NYC <- read.csv("D:/sfnyc/top2016NYC.csv")

top2016NYC_10 <- top2016NYC %>%
                  slice(1:10)

tbl_df(top2016NYC_10)



```

## HEAT/HOT WATER

### What does that entail? 

Get the descriptors:

```{sql sql_bulky_items_descriptor}
#standardSQL
SELECT
complaint_type,
descriptor,
COUNT(descriptor) AS total_count_descriptor
FROM
`bigquery-public-data.new_york.311_service_requests`
WHERE 
complaint_type = "HEAT/HOT WATER"
and EXTRACT(year from created_date) = 2016
GROUP BY complaint_type, descriptor
ORDER BY
2 DESC

```

What are the descriptors:

```{r bulky_items_descriptor}

h_desc <- read.csv("D:/sfnyc/heat_hw_desc.csv")

h_desc <- h_desc %>%
            arrange(desc(total_count_descriptor))

tbl_df(h_desc)


```

## NYC 2016 - Longitudes and Latitudes for Bulky Items

### Get results
The where condition pulled segments of the results, because BigQuery wouldn't allow larger downloads.

```{sql sql_monthly_long_lat}

#standardSQL
SELECT
complaint_type,
longitude, 
latitude,
COUNT(descriptor) AS total_count_descriptor
FROM
`bigquery-public-data.new_york.311_service_requests`
WHERE 
complaint_type = "Bulky Items"
and EXTRACT(year from created_date) = 2016
and EXTRACT(month from created_date) = 3
and longitude != 0
GROUP BY complaint_type, descriptor,longitude, latitude
ORDER BY
2 DESC


```


### Read results

Read in segmented files and combine
```{r bulky_items_descriptor}

nyb1 <- read.csv("D:/sfnyc/month1.csv")
nyb2 <- read.csv("D:/sfnyc/month2.csv")
nyb3 <- read.csv("D:/sfnyc/month3.csv")
nyb4 <- read.csv("D:/sfnyc/month4.csv")
nyb5 <- read.csv("D:/sfnyc/month5.csv")
nyb6 <- read.csv("D:/sfnyc/month6.csv")
nyb7 <- read.csv("D:/sfnyc/month7.csv")
nyb8_11 <- read.csv("D:/sfnyc/months8-11.csv")
nyb12 <- read.csv("D:/sfnyc/month12.csv")

nyba <- rbind(nyb1, nyb2, nyb3, nyb4, nyb5, nyb6, nyb7, nyb8_11, nyb12)

nyba <- nyba %>%
          arrange(desc(total_count))

tbl_df(nyba)

sum(nyba$total_count)

# t1 <- read.csv("D:/sfnyc/first16K.csv")
# t2 <- read.csv("D:/sfnyc/second16K.csv")
# t3 <- read.csv("D:/sfnyc/third16K.csv")
# 
# t1 <- read.csv("D:/sfnyc/t1.csv")
# t2 <- read.csv("D:/sfnyc/t2.csv")
# t3 <- read.csv("D:/sfnyc/t3.csv")
# 
# 
# 16000+16000+4488
# 
# ta <- rbind(t1, t2, t3)
# 
# sum(ta$total_count)
# 
# ta$dup <- duplicated(ta)
# 
# table(ta$dup)

```


## Read in NYC Shapefile

Read in shapefile, get list of neighborhoods and their coordinates to include as text labels

```{r sf_shapefile}

ny <-readOGR("D:/nybb_17a","nybb")

ny_wgs84 <- spTransform(ny, CRS("+proj=longlat +datum=WGS84"))

ny_wgs84@data$id = rownames(ny_wgs84@data)
ny_wgs84.points = fortify(ny_wgs84, region="id")
ny_wgs84.df = join(ny_wgs84.points, ny_wgs84@data, by="id")
ny_wgs84.df

tbl_df(ny_wgs84.df)

idList <- ny_wgs84@data$BoroName
# "coordinates" extracts centroids of the polygons, in the order listed at worldMap@data
centroids.df <- as.data.frame(coordinates(ny_wgs84))
names(centroids.df) <- c("Longitude", "Latitude")  #more sensible column names
# This shapefile contained population data, let's plot it.
#popList <- worldMap@data$POP2005

id.df <- data.frame(id = idList, centroids.df)

tbl_df(id.df)

# ggplot(ny_wgs84.df) + 
#   aes(long,lat,group=group) + 
#   geom_polygon() +
#   geom_path(color="white") +  
#   coord_equal() 

```

## Plot count of complaints by longitude and latitude, and map

```{r long_lat_comp_map}

ny_hhw <- ggplot(nyba, aes(longitude, latitude))  + #"id" is col in your df, not in the map object 
  expand_limits(x = ny_wgs84.df$long, y = ny_wgs84.df$lat) + 
  geom_polygon(data= ny_wgs84.df, aes(x=long, y=lat, group=group), fill="white", color="pink", size=0.15) +
  geom_point(aes(color=total_count, size=total_count, alpha=total_count) ) + 
  geom_text(data=id.df, aes(label = id, x = Longitude, y = Latitude), size=3) +
  labs(x = "Longitude", y = "Latitude", title = "NYC-Heat/Hot Water") + 
  scale_colour_gradient(low = "#ffb2b2", high = "black")
ny_hhw

table(nyba$total_count)
summary(nyba)




```

